### 2018-03-15 paper/4-build.tex
Add TODOs for S4

An alternative way to determine if a key is dirty is to record what state the values/hashes of dependencies were used at last time, and if something has changed, the key is dirty and must be recomputed - in essence a trace with which we can use to \textit{verify} existing values. We can describe a trace as:

\begin{minted}{haskell}
data Trace k v = Trace
    {key :: k
    ,dependencies :: [(k, Hash v)]
    ,result :: Hash v
    }
\end{minted}

We assume that \hs{Hash v} is a small constant size, constructed from hashing the underlying \hs{v} rather than storing it directly. Checking a trace requires ensuring all the dependencies are up-to-date (using whatever ordering strategy as per \S\ref{sec-dependency-orderings}), then comparing if the dependencies are same as the current value and that the result is the same. After computing a fresh value we add its \hs{Trace} to the list. Therefore the information stored by a build system that verifies traces is \hs{[Trace k v]}.

@@

\begin{minted}{haskell}
data Traces k v = Traces
    {traces :: [Trace k v]
    ,contents :: Map (Hash v) v
    }
\end{minted}

We have a list of traces, plus a \hs{Map} from the hash to the actual contents. Checking a trace is the same as before, but if the result is the only thing that is different we can simply retrieve a fresh result from \hs{contents} \textit{without} recomputing it.

@@

\todo{AM}{AM: I would also like to see an actual \hs{upToDate} function for verifying, and a \hs{recreate} for `recreating'. NM: It actually gets a bit more confusing than that - since you end up needing to pass functions to get yourself, your dependencies etc. Unclear there is a win. The functions would occur in the next section anyway.}

>>>>

An alternative way to determine if a key is dirty is to record what state the
values/hashes of dependencies were used at last time, and if something has
changed, the key is dirty and must be recomputed -- in essence a \emph{trace}
which we can use to \textit{verify} existing values. We can describe a trace as:

\todo{AM/NM}{Change from \hs{[Trace k v]} to \hs{Map k (Trave k v)} or something
similar, so that it's obvious we have one trace per key .}

\begin{minted}{haskell}
data Trace k v = Trace
    { key          :: k
    , dependencies :: [(k, Hash)]
    , result       :: Hash }
\end{minted}

We assume that \hs{Hash} is a small constant size, constructed from hashing the
underlying \hs{v} rather than storing it directly. Checking a trace requires
ensuring all the dependencies are up-to-date (using whatever ordering strategy
as per \S\ref{sec-dependency-orderings}), then comparing if the dependencies are
same as the current value and that the result is the same. After computing a
fresh value we add its \hs{Trace} to the list. Therefore the information stored
by a build system that verifies traces is \hs{[Trace k v]}.

@@

\todo{AM/NM}{Traces -- why the indirection (first get the hash, then look it up)?
Can we drop it? Can we switch to a more efficient/explicit data structure than a list?}

\begin{minted}{haskell}
data Traces k v = Traces
    { traces :: [Trace k v]
    , cache  :: Map Hash v }
\end{minted}

We have a list of traces, plus a \hs{Map} from the hash to the actual contents. Checking a trace is the same as before, but if the result is the only thing that is different we can simply retrieve a fresh result from \hs{cache} \textit{without} recomputing it.

@@

\todo{AM}{AM: I would also like to see actual \hs{verify} and \hs{construct} functions.

NM: It actually gets a bit more confusing than that - since you end up needing to pass functions to get yourself, your dependencies etc. Unclear there is a win. The functions would occur in the next section anyway.

AM: Now, after we've switched to \hs{Store i k v} it might work better?}
